---
title: "Exploring the use of syntactic superlatives on Twitter"
output:
  pdf_document: default
  html_notebook: default
---

## Data

Counts for *'de/het meest \*e'* (syntactic superlative) and *'de/het \*ste'* (morphological superlative) per month for 2013-2020 Dutch twitter data. 

For the morphological data, we filtered occurrences of *'eerste, laatste, meeste, juiste, beste'* as these are very frequent (approx. 60% of the cases) while the syntactic alternative does not really exist. 

Note that we did not filter retweets, this might have some effect especially for counts of specific word forms. 

Loading the raw counts: 

```{r}
library(dplyr)
setwd("C:/Users/gosse/haytabo/CorpusLinguistics")
meest <- read.csv("meest_super.csv", sep=' ')
meestt <- tibble(meest) 
meestt

```

## Adding some rows

Adding rows for total and ratio of meest/super and percentage of *meest* in total

```{r}

meestt2 <- mutate(meestt, total = meest + super, ratio = meest/super, percentage = meest/total)
meestt2
       
```
## Plotting the trend

```{r}
library(ggplot2)

ggplot(data = meestt2, aes(x=as.Date(Month), y = ratio)) + geom_col() + geom_smooth(method = "lm") +
    coord_cartesian(ylim = c(0.0,0.2)) + xlab('Month') + ggtitle("Ratio of syntactic over synthetic superlatives")


ggplot(data = meestt2, aes(x=as.Date(Month), y = percentage)) + geom_col() + geom_smooth(method = "lm") +
    coord_cartesian(ylim = c(0.0,0.2)) + xlab('Month') + ggtitle("Percentage of syntactic superlatives")

```


## Individual forms

Does this trend also hold when we check for individual forms. Here we try *'meest populaire'* vs *'populairste'*. 

It seems the trend is in the same direction, but the data is quite a bit more noisy, due to lower total numbers. 

```{r}
populair <- read.csv("meest_populaire.csv", sep=' ')
populairr <- tibble(populair) 
populairr2 <- mutate(populairr, total = meest + super, ratio = meest/super, percentage = meest/total)
populairr2

ggplot(data = populairr2, aes(x=as.Date(Month), y = ratio)) + geom_col() + geom_smooth(method = "lm") +
    xlab('Month') + ggtitle("Ratio of syntactic over synthetic superlatives")
```

## Prefix aller-

The prefix *aller-* is quite popular in the superlative as well (*allerliefste*). Does it increase in popularity as well? Here we compare counts for *aller-* prefixed superlatives with all superlatives.

The trend is downward. (Quick hypothesis: as Twitter is being used more and more for professional communication, informal language decreases as well. We see this with other phenomena as well, such as frequency of spelling errors. )

```{r}
aller <- read.csv("aller.csv", sep=' ')
allerr <- tibble(aller) 
allerr2 <- mutate(allerr,  percentage = aller/super)
allerr2

ggplot(data = allerr2, aes(x=as.Date(Month), y = percentage)) + geom_col() + geom_smooth(method = "lm") +
    xlab('Month') + ggtitle("Percentage of aller- in synthetic superlatives")
```
```

